---
title: "Gap Analysis"
author: "Caleb Aguiar"
date: "4/1/2021"
output: word_document
---

```{r setup, include=FALSE}
#install.packages("remotes")
#remotes::install_github("ajdamico/lodown")

library(lodown) #R package to download large files 

library(ggplot2)
```

## Load Survey of Consumer Finances

Dataset here:https://www.federalreserve.gov/econres/scfindex.htm

```{r,  include=FALSE}
scf_cat <-
    get_catalog( "scf" ,
        output_dir = file.path( path.expand( "~" ) , "SCF" ) )


scf_cat <- subset( scf_cat , year == 2019 )
# download the microdata to your local computer
scf_cat <- lodown( "scf" , scf_cat )
```

## Prevent overestimation of standard error calculations in regression    

Please review the following PDF for instructions on how to calculate correct standard errors. As a result of multiple imputation, the dataset you are downloading contains five times the number of actual observations. Failure to account for the imputations and the complex sample design will result in incorrect estimation of standard errors.
https://www.federalreserve.gov/econres/files/Standard_Error_Documentation.pdf

The following code accounts for imputation and sample variability error, and constructs a multiply-imputed, complex sample survey design. 

```{r, include=FALSE}
library(survey)
library(mitools)

scf_imp <- readRDS( file.path( path.expand( "~" ) , "SCF" , "scf 2019.rds" ) )

scf_rw <- readRDS( file.path( path.expand( "~" ) , "SCF" , "scf 2019 rw.rds" ) )

scf_design <- 
    svrepdesign( 
        weights = ~wgt , 
        repweights = scf_rw[ , -1 ] , 
        data = imputationList( scf_imp ) , 
        scale = 1 ,
        rscales = rep( 1 / 998 , 999 ) ,
        mse = FALSE ,
        type = "other" ,
        combined.weights = TRUE
    )
```
## Variable Recoding

```{r}
scf_design <- 
    update( 
        scf_design , 
        
        hhsex = factor( hhsex , labels = c( "male" , "female" ) ) ,
        
        married = as.numeric( married == 1 ) ,
        
        edcl = 
            factor( 
                edcl , 
                labels = 
                    c( 
                        "less than high school" , 
                        "high school or GED" , 
                        "some college" , 
                        "college degree" 
                    ) 
            ),
        racecl4 = 
            factor( 
                racecl4 , 
                labels = 
                    c( 
                        "White" , 
                        "Black.AfricanAmer" , 
                        "Hispanic.Latino" , 
                        "Other" 
                    ) 
            )

    )


  
```

## Unweighted Counts
Count the unweighted number of records in the survey sample, overall and by groups

```{r}
scf_MIcombine( with( scf_design , svyby( ~ one , ~ one , unwtd.count ) ) )

scf_MIcombine( with( scf_design , svyby( ~ one , ~ hhsex , unwtd.count ) ) )

barplotdf<-scf_MIcombine( with( scf_design , svyby( ~ one , ~ racecl4 , unwtd.count ) ) )

scf_MIcombine( with( scf_design , svyby( ~ one , ~ edcl , unwtd.count ) ) )

```

```{r}
barplot(barplotdf$coefficients)
```




## Weighted Counts
```{r}
scf_MIcombine( with( scf_design , svytotal( ~ one ) ) )

scf_MIcombine( with( scf_design ,
    svyby( ~ one , ~ racecl4 , svytotal )
) )

```


# Descriptive Statistics

## Calculate the mean (average) of a linear variable, overall and by groups and then plot:

```{r, include=FALSE}
scf_MIcombine( with( scf_design , svymean( ~ networth ) ) )

networthdt<-scf_MIcombine( with( scf_design ,
    svyby( ~ networth , ~ racecl4 , svymean )
) )

```

```{r}
options(scipen = 999) 
barplot(networthdt$coefficients, names.arg = c("White", "Black", "Hispanic", "Other"), ylab = "Ave Net Worth", col = "Steel Blue")
```
White families have more wealth than Black, Hispanic and other race families, on average.

## Calculate the median by groups:

```{r, include=FALSE}
scf_MIcombine( with( scf_design ,
    svyquantile(
        ~ networth ,
        0.5 , se = TRUE , method = 'constant' , interval.type = 'quantile' 
) ) )

networthmedian<-scf_MIcombine( with( scf_design ,
    svyby(
        ~ networth , ~ racecl4 , svyquantile ,
        0.5 , se = TRUE , method = 'constant' , interval.type = 'quantile' ,
        keep.var = TRUE , ci = TRUE 
) ) )
```

```{r}
barplot(networthmedian$coefficients, names.arg = c("White", "Black", "Hispanic", "Other"), ylab = "Median Net Worth", col = "Steel Blue")
```

White families have more wealth than Black, Hispanic and other race families, when looking at the median net worth, although it is less, which shows that extremely wealthy white families skew the results.






## Calculate the distribution of a categorical variable, overall and by groups:

```{r}
scf_MIcombine( with( scf_design , svymean( ~ edcl ) ) )

edplotdt<-scf_MIcombine( with( scf_design ,
    svyby( ~ edcl , ~ racecl4 , svymean )
) )

```
```{r}
par(mar=c(15,4,4,2))
barplot(sort(edplotdt$coefficients, decreasing = TRUE), col = "Orange", las=2)

```



Function for ggplot and survey results
Would like to use ggplot here, make the graphs cleaner.
https://juba.github.io/questionr/reference/ggsurvey.html


```{r}
ggsurvey <- function(design = NULL, mapping = NULL, ...) {
  if (!inherits(design, "survey.design")) {
    stop("'design' should be a 'survey.design' object.")
  }
  if (!requireNamespace("survey", quietly = TRUE)) {
    stop("survey package is required.")
  }
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("ggplot2 package is required.")
  }
  data <- design$variables
  data$.weights <- weights(design)
  
  if(is.null(mapping)) {
    mapping <- ggplot2::aes()
  }
  
  mapping$weight <- ggplot2::aes_string(weight = ".weights")$weight
  
  ggplot2::ggplot(data, mapping, ...)
}
```


```{r}
#ggsurvey(design = scf_design, mapping = aes(x = , y = ))
```


